Bootstrapping Multi-atlas Hippocampal Segmentation with MAGeT

### 2013-03-28 paper.Rnw

ggplot(subset(all_data, method == 'majvote'), 
       aes(x=templates.y,y=k.y, colour=as.factor(atlases))) + 
  facet_grid(reg_method~method.y) + 
  #stat_summary(fun.y=mean,geom='line',
  #             aes(y=k.y)) + 
  stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" )
@
  \caption{MAGeT brain mean DSC by atlas and template library size}
  \label{fig:ADNI1_xval-k_mean}
\end{figure}

@@

\begin{figure}
<<ADN1-Xval-k-diff, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
ggplot(subset(all_data, reg_method=="ANTS" & method.y=="Majority Vote"), 
       aes(x=templates.y, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  stat_summary(fun.data=mean_cl_boot,geom='errorbar',
               aes(y=k_diff,colour=as.factor(atlases), width=0.2)) +
  stat_summary(fun.y=mean, geom="point", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  #stat_smooth(method=lm, formula=y~log(x)) + 
  geom_hline(aes(alpha=0.5, yintercept=0), linetype='dashed') + 
  coord_cartesian(ylim=c(-0.1,0.05)) + 
  scale_x_continuous(breaks=1:20) + scale_y_continuous(breaks=seq(-1,1,by=0.01)) + 
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(legend=FALSE) + 
  scale_linetype_discrete(legend=FALSE) + 
  xlab( "Number of Templates" ) + 
  ylab( "Increase in mean Kappa between MAGeT brain and multiatlas" ) 
@
  \caption{Increase in mean Kappa between MAGeT brain and multi-atlas}
  \label{ADNI1_cross_validation_MA_difference}
\end{figure}

@@

stddev = ddply(ANTSmajvote, c("subject", "label","atlases","templates.y"), function (df) {
  data.frame(
    MA = sd(df$k.x),
    MB = sd(df$k.y) 
  )
})

stddev.t.test = ddply(stddev, c("atlases","templates.y"), function (df) {
  t = t.test(df$MA, df$MB)
  data.frame(
    statistic = t$statistic, 
    p.value = t$p.value
  )
})

ggplot(stddev.t.test, 
       aes(x=templates.y, y=p.value, colour=as.factor(atlases))) + 
  geom_line() + 
  geom_hline(aes(yintercept=0.05), linetype='dashed') + 
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide='none') + 
  scale_linetype_discrete(guide='none') + 
  scale_x_continuous(breaks=1:20) + scale_y_continuous(breaks=seq(0,1,by=0.05)) + 
  xlab( "Number of Templates" ) + 
  ylab( "p-value" ) 
@
\end{figure}

>>>>

ggplot(subset(all_data, method == 'majvote'), 
       aes(x=templates.y,y=k.y, colour=as.factor(atlases))) + 
  facet_grid(reg_method~method.y) + 
  stat_summary(fun.y=mean,geom='line',
               aes(y=k.y, weight=1)) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" )
@
  \caption{MAGeT brain mean DSC by atlas and template library size}
  \label{fig:ADNI1_xval-k_mean}
\end{figure}

@@

\begin{figure}
<<ADN1-Xval-k-diff, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
ggplot(subset(all_data, reg_method=="ANTS" & method.y=="Majority Vote" &
                templates.y %in% seq(1,20,2)), 
       aes(x=templates.y, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  stat_summary(fun.data=mean_cl_boot,geom='errorbar',
               aes(y=k_diff,colour=as.factor(atlases), width=0.2)) +
  stat_summary(fun.y=mean, geom="point", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_summary(fun.y=mean, geom="line", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  #stat_smooth(method=lm, formula=y~log(x)) + 
  geom_hline(aes(alpha=0.5, yintercept=0), linetype='dashed') + 
  coord_cartesian(ylim=c(-0.1,0.05)) + 
  scale_x_continuous(breaks=seq(1,20,2)) + scale_y_continuous(breaks=seq(-1,1,by=0.01)) + 
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(legend=FALSE) + 
  scale_linetype_discrete(legend=FALSE) + 
  xlab( "Number of Templates" ) + 
  ylab( "Increase in mean Kappa between MAGeT brain and multiatlas" ) 
@
  \caption{Increase in mean Kappa between MAGeT brain and multi-atlas}
  \label{ADNI1_cross_validation_MA_difference}
\end{figure}

@@

data.stats = ddply(ANTSmajvote, c("subject", "label","atlases","templates.y"), function (df) {
  data.frame(
    MA.sd  =  sd(df$k.x),
    MB.sd  =  sd(df$k.y),
    MA.var = var(df$k.x),
    MB.var = var(df$k.y)    
  )
})

stats.tests = ddply(data.stats, c("atlases","templates.y"), function (df) {
  t.var = t.test(df$MA.var, df$MB.var)
  t.sd  = t.test(df$MA.sd , df$MB.sd)
  data.frame(
    stat      = c("var", "sd"),
    statistic = c(t.var$statistic, t.sd$statistic),
    p.value   = c(t.var$p.value, t.sd$p.value)
  )
})

ggplot(stats.tests, 
       aes(x=templates.y, y=p.value, colour=as.factor(atlases))) + 
  facet_grid( . ~ stat) + 
  geom_line() + 
  geom_hline(aes(yintercept=0.05), linetype='dashed') + 
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide='none') + 
  scale_linetype_discrete(guide='none') + 
  scale_x_continuous(breaks=1:20) + scale_y_continuous(breaks=seq(0,1,by=0.05)) + 
  xlab( "Number of Templates" ) + 
  ylab( "p-value" )

@
\end{figure}

<<ADN1-Xval-sd-by-subject, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
SDs = data.stats[c('subject','label','atlases','templates.y','MA.sd','MB.sd')]
SDs = subset(SDs, templates.y %in% c(5,10,15,20) & atlases == 5)

melted = melt(SDs, measure.vars=c('MA.sd','MB.sd'))
ggplot(melted, aes(x=templates.y, y=value, 
                   group=interaction(templates.y, variable), colour=as.factor(variable))) + 
  scale_x_continuous(breaks=c(5,10,15,20)) + 
  geom_violin() 
@
